\documentclass[12pt]{article}
\usepackage[T1]{fontenc}
\usepackage{amssymb}
\usepackage{titlesec}
\usepackage{scrextend}
\usepackage{fancyhdr}
\usepackage{enumitem}
\usepackage[letterpaper, margin=.75in]{geometry}
\usepackage[scaled]{helvet}
\renewcommand\familydefault{\sfdefault}
\titleformat{\section}{}{$\square$ \thesection}{2em}{}
\fancyhf{}
\fancyfoot[L]{V0.0.1}
\fancyfoot[C]{\thepage}
\fancyfoot[R]{MRC:F:CL:0}
\begin{document}
\pagestyle{fancy}
\begin{center}
	{\center \Large Mines Rocket Club FAR Higher Launch Prep Checklist}\newline
\end{center}
\begin{tabular}{lclc}
	Flyer Name    & \framebox[45mm]{\rule{0pt}{7.5mm} Will Swegles} & Launch Date & \framebox[45mm]{\rule{0pt}{7.5mm} 2024-6-15}\\
	Overseer Name & \framebox[45mm]{\rule{0pt}{7.5mm}} & Rocket Name & \framebox[45mm]{\rule{0pt}{7.5mm} FAR Higher}\\
\end{tabular}
\section*{Notes}
\framebox[7in]{\rule{0pt}{2in}}
\section*{Avionics Configuration}
\begin{tabular}{lclc}
	Computer Model    & \framebox[45mm]{\rule{0pt}{7.5mm}} & Serial Number & \framebox[45mm]{\rule{0pt}{7.5mm}}\\
	Drouge Delay    & \framebox[45mm]{\rule{0pt}{7.5mm}} & Drouge Charge Size & \framebox[45mm]{\rule{0pt}{7.5mm}}\\
	Main Altitude & \framebox[45mm]{\rule{0pt}{7.5mm}} & Main Charge Size & \framebox[45mm]{\rule{0pt}{7.5mm}}\\
	Callsign & \framebox[45mm]{\rule{0pt}{7.5mm}} & Channel / Frequency & \framebox[45mm]{\rule{0pt}{7.5mm}}\\
	Orientation & \framebox[45mm]{\rule{0pt}{7.5mm}} & Baudrate & \framebox[45mm]{\rule{0pt}{7.5mm}}\\
\end{tabular}
\section{Pre-Departure / Hotel Room}
\begin{addmargin}[3em]{3em}
	\begin{enumerate}[label=\thesection.\arabic*\quad$\square$]
		\item Test of all pyro charges (Pop Test, inclues test firing second stage ignitor).
		\item Test fit of avionics and batteries.
		\item Test recovery deployment via pull test.
		\item Construct, label, and store pyro charges.
		\item Ensure good fit of motor into motor mount and casing retention system.
		\item Ensure presence of 2x launch rail guide system.
		\begin{enumerate} [label=\thesection.\arabic{enumi}.\arabic*\quad$\square$]
			\item Flyaways
			\item Lugs
			\item Tower
		\end{enumerate}
		\item Ensure appropriate paperwork
		\begin{enumerate} [label=\thesection.\arabic{enumi}.\arabic*\quad$\square$]
			\item Club Flight Card
			\item Site Flight Card
		\end{enumerate}
	\end{enumerate}
\end{addmargin}
\section{Departure}
\begin{addmargin}[3em]{3em}
	\begin{enumerate}[label=\thesection.\arabic*\quad$\square$]
		\item Ensure all rocket components are together and labelled.
		\item Ensure that all of the rocket's recovery devices are integrated into the rocket.
		\item Ensure the presence of the telemega in the avionics bay with a charged battery and a pyro batter and pyro battery holder.
		\item Ensure charges are packed correctly and labelled.
		\item Ensure presence of avionics screwdrivers.
		\item If using flyaway rail guides, ensure presence.
	\end{enumerate}
\end{addmargin}
\section{Preflight}
\begin{addmargin}[3em]{3em}
	\begin{enumerate}[label=\thesection.\arabic*\quad$\square$]
		\item Ensure rail guides are installed.
		\item Collect pyro charges from pyro box.
		\item Install pyro charges (do not arm the flight computer).
		\item Check continuity, avionics functionality, GPS lock, and radio signal with avionics in idle mode.
		\item Ensure airframe is undamaged.
		\item Ensure motor mounts \& retention is undamaged.
		\item Install motors, checking head end retention, closure secureness, and lack of wiggle in grains.
		\item Plug in and check functionality of screamer. Return to CF tube as quickly as possible.
		\item Notify club members of immenent launch. Begin moratorium on other club flights.
		\item Check in with site RSO and/or Safety Officer
	\end{enumerate}
\end{addmargin}
\section{On Pad}
\begin{addmargin}[3em]{3em}
	\begin{enumerate}[label=\thesection.\arabic*\quad$\square$]
		\item Approach the rail.
		\item Install rocket onto launch rail.
		\item Orient the launch rail for launch.
		\item Activate \& arm the avionics.
		\item Check with base station for connectivity, GPS lock, and flight state.
		\item Retreat to the launch control area.
		\item Before launch:
		\begin{enumerate} [label=\thesection.\arabic{enumi}.\arabic*\quad$\square$]
			\item Double check roles of visual and telemetry tracking for both booster and sustainer.
			\item Confirm search groups for each stage
			\item Ensure telemetry computer has a power supply attatched
		\end{enumerate}
		\item Upon launch:
		\begin{enumerate} [label=\thesection.\arabic{enumi}.\arabic*\quad$\square$]
			\item Sustainer telemetry: communicate alittude and major events to club and RSO.
			\item Booster telemetry begin tracking upon staging event.
			\item Booster visual continue watching the booster until ground hit and filming if possible.
		\end{enumerate}
		\item Enter GPS coordinates of sustainer into GPS and phones of sustainer search party.
		\item Ensure that both search patries have adequate food \& water.
		\item Ensure both parties have radio communication with the base staion \& depart. 
	\end{enumerate}
\end{addmargin}
\section{Recovery}
\begin{addmargin}[3em]{3em}
	\begin{enumerate}[label=\thesection.\arabic*\quad$\square$]
		\item Take pictures of the rocket as found.
		\item Collect all components of the rocket, as well as any waste that can be found.
		\item If using avionics, deactivate and disarm.
		\item Ensure the casing is still present and undamaged.
		\item Take a visual inspection of the rocket.
		\item Communicate to base station that the rocket has been recovered and the status of the casing and airframe.
	\end{enumerate}
\end{addmargin}
\end{document}
