\documentclass[12pt]{article}
\usepackage[T1]{fontenc}
\usepackage{amssymb}
\usepackage{titlesec}
\usepackage{scrextend}
\usepackage{fancyhdr}
\usepackage{enumitem}
\usepackage[letterpaper, margin=.75in]{geometry}
\usepackage[scaled]{helvet}
\renewcommand\familydefault{\sfdefault}
\titleformat{\section}{}{$\square$ \thesection}{2em}{}
\fancyhf{}
\fancyfoot[L]{V0.0.1}
\fancyfoot[C]{\thepage}
\fancyfoot[R]{MRC:F:CL:0}
\begin{document}
\pagestyle{fancy}
\begin{center}
	{\center \Large Mines Rocket Club General  Launch Preparation Checklist}\newline
\end{center}
\begin{tabular}{lclc}
	Flyer Name    & \framebox[45mm]{\rule{0pt}{7.5mm}} & Launch Date & \framebox[45mm]{\rule{0pt}{7.5mm}}\\
	Overseer Name & \framebox[45mm]{\rule{0pt}{7.5mm}} & Rocket Name & \framebox[45mm]{\rule{0pt}{7.5mm}}\\
\end{tabular}
\section*{Notes}
\framebox[7in]{\rule{0pt}{2in}}
\section*{Avionics Configuration}
\begin{tabular}{lclc}
	Computer Model    & \framebox[45mm]{\rule{0pt}{7.5mm}} & Serial Number & \framebox[45mm]{\rule{0pt}{7.5mm}}\\
	Drouge Delay    & \framebox[45mm]{\rule{0pt}{7.5mm}} & Drouge Charge Size & \framebox[45mm]{\rule{0pt}{7.5mm}}\\
	Main Altitude & \framebox[45mm]{\rule{0pt}{7.5mm}} & Main Charge Size & \framebox[45mm]{\rule{0pt}{7.5mm}}\\
	Callsign & \framebox[45mm]{\rule{0pt}{7.5mm}} & Channel / Frequency & \framebox[45mm]{\rule{0pt}{7.5mm}}\\
	Orientation & \framebox[45mm]{\rule{0pt}{7.5mm}} & Baudrate & \framebox[45mm]{\rule{0pt}{7.5mm}}\\
\end{tabular}
\section{Pre-Departure}
\begin{addmargin}[3em]{3em}
	\begin{enumerate}[label=\thesection.\arabic*\quad$\square$]
		\item Test of all pyro charges (Pop Test).
		\item Test fit of avionics and batteries.
		\item Test recovery deployment via pull test.
		\item Construct, label, and store pyro charges.
		\item Ensure good fit of motor into motor mount and casing retention system.
		\item Ensure presence of launch rail guide system.
		\begin{enumerate} [label=\thesection.\arabic{enumi}.\arabic*\quad$\square$]
			\item Flyaways
			\item Lugs
			\item Tower
		\end{enumerate}
		\item Ensure appropriate paperwork
		\begin{enumerate} [label=\thesection.\arabic{enumi}.\arabic*\quad$\square$]
			\item Certification Paperwork
			\item Club Flight Card
			\item Site Flight Card
		\end{enumerate}
	\end{enumerate}
\end{addmargin}
\section{Departure}
\begin{addmargin}[3em]{3em}
	\begin{enumerate}[label=\thesection.\arabic*\quad$\square$]
		\item Ensure all rocket components are together and labelled.
		\item Ensure that all of the rocket's recovery devices are present if not already integrated into the rocket.
		\item Ensure that all electronics and electronics support equipment needed is present.
		\item If using pyro charges, ensure charges are packed correctly and labelled.
		\item If tools are needed onsite, ensure they are present and packed to avoid damage.
		\item If using flyaway rail guides, ensure presence.
	\end{enumerate}
\end{addmargin}
\section{Preflight}
\begin{addmargin}[3em]{3em}
	\begin{enumerate}[label=\thesection.\arabic*\quad$\square$]
		\item Ensure rail guides are installed.
		\item Ensure avionics are functional outside rocket. 
		\item Ensure airframe is undamaged.
		\item Ensure motor mounts \& retention is undamaged.
		\item Install avionics.
		\item Construct motor per motor assembly guides.
		\item Install motor.
		\item Collect pyro charges from pyro box.
		\item Install pyro charges (do not arm the flight computer).
		\item Collect flight-time paperwork from paperwork storage.
		\item Check out with Club Safety Officer
		\item Check in with site RSO and/or Safety Officer
	\end{enumerate}
\end{addmargin}
\section{On Pad}
\begin{addmargin}[3em]{3em}
	\begin{enumerate}[label=\thesection.\arabic*\quad$\square$]
		\item Approach the rail.
		\item Install rocket onto launch rail.
		\item Orient the launch rail for launch.
		\item Activate \& arm the avionics.
		\item If telemetry is present, check with base station for connectivity.
		\item Retreat to the launch control area.
		\item Upon launch:
		\begin{enumerate} [label=\thesection.\arabic{enumi}.\arabic*\quad$\square$]
			\item Assign a person for visual tracking.
			\item If using telemetry, communicate with the telemetry base station for position data.
			\item Wait for ground hit.
			\item Collect tracking information from visual tracking and others.
		\end{enumerate}
		\item Ensure recovery party has radion communication with the base staion \& depart. 
	\end{enumerate}
\end{addmargin}
\section{Recovery}
\begin{addmargin}[3em]{3em}
	\begin{enumerate}[label=\thesection.\arabic*\quad$\square$]
		\item Take pictures of the rocket as found.
		\item Collect all components of the rocket, as well as any waste that can be found.
		\item If using avionics, deactivate and disarm.
		\item Ensure the casing is still present and undamaged.
		\item Take a visual inspection of the rocket.
		\item Communicate to base station that the rocket has been recovered and the status of the casing and airframe.
	\end{enumerate}
\end{addmargin}
\end{document}
