\documentclass[12pt]{article}
\usepackage{times}
\usepackage{sectsty}
%%\renewcommand{\thesection}{Article \Roman{section}}
%\renewcommand{\theparagraph}{(\arabic{paragraph})}
%\renewcommand{\thesubparagraph}{(\alph{subparagraph})}
\newcommand{\note}[1]{\raisebox{.5em}{\small Note #1}}
\setcounter{secnumdepth}{9}
\setcounter{tocdepth}{9}
\usepackage{todonotes}
\usepackage[letterpaper, margin = 1.5in]{geometry}
\usepackage{color, soul}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{cleveref}
\usepackage{datetime2}
\begin{document}
\noindent{\Huge \bf \fontfamily{phv}\selectfont Mines Rocket Club Policies}\newline

\noindent{\Large \fontfamily{phv}\selectfont Revised \DTMtoday\ \DTMcurrenttime}
\clearpage
\tableofcontents
\clearpage
\section{Purpose}
As defined in The Rocket Club's bylaws, the goal of these policies are to:
\begin{enumerate}[label=(\roman*)]
    \item safe operation during lab meetings,
    \item safe operation during launches,
    \item effective utilization of club funding,
    \item cleanliness of the workspace, and,
    \item a positive and encouraging atmosphere.
\end{enumerate}
\section{Safety}
\subsection{General}
\subsection{Lab}
\subsection{Launches}
All members of The Mines Rocket Club (the `Club') shall abide by, in this order;
\begin{enumerate}[label=(\roman*)]
    \item the rulings of the Launch Director and Range Safety Officer \note{1,2};
    \item Tripoli Rocketry Association, Inc. Safety Code (TRA) \note{1};
    \item the club safety officer (CSO).
\end{enumerate}
Failiure to comply with settled regulation or ad-hoc rulings by the RSO or CSO will result in a repercussion defined by \cref{citation:s.general}.
\section{Expenditure}
\subsection{Operational Expenditures}
\subsubsection{Attrition}
As is the nature of the art, there are intrinsic risks to high-powered rocketry.
Due to the construction methods and materials typically used in The Mines Rocket Club,
the primary sources of attrition relevant to the club's operations are casings and avionics.
As such, a portion of the budget must be dedicated to replacing lost or destroyed casings and avionics.
\subsection{Event Expenditures}
In order to maintain good standing with SAIL and other regulatory bodies,
the Club is required to host several service events.

\subsection{Equipment Expenditures}
\section{Operations}
\subsection{Lab}
\subsubsection{Entry Procedures}

\subsubsection{Tool Use}
\subsubsection{Cleanup}
\subsubsection{Exit Procedures}
\subsection{Transport}
\subsection{Launches}
\subsubsection{Reasonable Notification}
\subsubsection{Launch Equipment Checkout List}
\subsubsection{Onsite Procedures}
\section{Repercussions}
\subsection{Major}
\subsection{Safety Violations}
\subsubsection{General}
\label{citation:s.general}
\paragraph{Adjudication}
This citation may be issued by the following parties:
\begin{enumerate}[label=(\roman*)]
    \item the Safety Officer \note{1},
    \item any officer. \newline
    Note 1: The Safety Officer may issue this citation at any point during a launch.
    The citation will stand for the duration of the launch, 
    and will be reviewed by the officers at the next meeting.
\end{enumerate}
\paragraph{Terms}
\label{safob}
The accused party will be placed under `Safety Observation' until the Safety Officer finds that the violating behavior has ceased.
Parties under Safety Observation must check in with the Safety Officer prior to undertaking any activities within The Rocket Club.

\subsection{Misappropriation}
\subsubsection{Applicability}
These citations may not be issued for the following events:
\begin{enumerate}[label=(\roman*)]
    \item usage of a rocket motor during a planned, Mines Rocket Club sanctioned launch or other event,
    \item loss of avionic equipment,
    \item loss of a motor casing.
\end{enumerate}
All of these cases are the intended use of Mines Rocket Club resources, and are therefore not punishable.
Parties responsible for the losses, especially to items (b) and (c) are encouraged to search for them on the site.
\subsubsection{Minor}
\paragraph{Definition}
Minor Misappropriation shall be defined as the removal, without intent of returning, 
of any item with a current value less than or equal to \$50.
\paragraph{Adjudication}
\label{misap:adj}
May be issued by any officer of The Mines Rocket Club with proper evidence.
\paragraph{Terms}
\label{misap:terms}
A request will be made of the offending party to return the removed item(s).
Failure to do so will result in escalation.
Until such time as the property has been retrieved,
the offending parties will be forbidden from placing club orders, 
and using club materials without direct permission of an officer.
This citation and its effects expire upon return of the removed materials.
\subsubsection{Major}
\paragraph{Definition}
Major Misappropriation shall be defined as the removal, without intent of returning,
of any item of a value greater than \$50.
\paragraph{Adjudication}
See \cref{misap:adj}.
\paragraph{Terms}
See \cref{misap:terms}.
\subsection{General Bans}
\label{citations:ban}
\subsubsection{Definition}
A `General Ban' prevents a party from participating in any Club activities.
\subsubsection{Adjudication}
May be issued upon vote of the leadership.
\paragraph{Terms}
The charged party is forbidden from: 
\begin{enumerate}[label=(\roman*)]
    \item colocation in the space which hosts the Club during club hours,
    \item utilization of Club materials and tools.
\end{enumerate}
\section{Interoperability}
\end{document}